Computer Science House Constitution

### 2024-10-04 constitution.tex
prevent the number of eligible votes from changing during the execution of a vote

\asubsection{Introductory Membership Qualifications}
Intro Membership is open to all students currently enrolled at RIT.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.

>>>>

\asubsection{Introductory Membership Qualifications}
Intro Membership is open to all students currently enrolled at RIT, excluding all Active and Alumni Members.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.
The number of Eligible Votes is determined when a vote is called and remains fixed throughout the duration of the vote.
